Dissertation

### 2024-04-15 Manuscript/manuscript.qmd
fix overflowing table 15

::: {#tbl-e3-bmm-dist}
| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
| **conditVaried:bandTypeExtrapolation**                  |    52.66 |         14.16 |         90.23 | 1.00 |
| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
| conditVaried:bandTypeExtrapolation:bandOrderReverse |    30.42 |        -21.00 |         81.65 | 0.87 |

>>>>

::: {#tbl-e3-bmm-dist}
| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
| **conditVaried:bandTypeExtrapolation**                  |    52.66 |         14.16 |         90.23 | 1.00 |
| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
| conditVaried:bandTypeExtrapolation:bandOrder |    30.42 |        -21.00 |         81.65 | 0.87 |
